Supermartingales and Termination Analysis of Statistical PCF

### 2021-11-26 LICS21/related.tex
Update because the completeness conjecture is false

\subsection*{Further directions} We have not yet been able to prove Conjecture~\ref{conj:antitone} which would imply that Theorem~\ref{thm:antitone rankable implies termination} is almost complete.
\begin{conjecture}[Completeness]
\label{conj:antitone}
If every term reachable from a certain PPCF term is AST, then that term is antitone rankable.
\end{conjecture}

>>>>

\subsection*{Further directions} All of the variants of the method we have presented for proving almost sure termination are incomplete, being unable to deal with terms like Example \ref{ex:antitone isn't complete}, so extending it to be applicable to more terms would likely be possible.
